Reproducibility in Plant Pathology

### 2020-04-21 README.rmd
cleanup duplicated information in README for licences
Use doi2bib package

# Reproducibility in Plant Pathology

[![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

@@

This repository is organized as an R package. There is one R function,
`doi2bib()`, that is used in this repository, along with a bibliography file of
the articles that were examined that are located in `inst/extdata` directory. We
have used the R package structure to help manage dependencies, to take advantage
of continuous integration for automated code testing and for file organisation.

@@

### Licenses

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

>>>>

# Reproducibility in Plant Pathology
![Publish Docker](https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/workflows/Publish%20Docker/badge.svg)
[![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

@@

This repository is organized as an R package. There are custom R functions, 
`table_of_journals()` and `workflow_dia()` that are used in this repository, along with a bibliography file of the articles that were examined and the notes that are located in `inst/extdata` directory.
We have used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing and for file organisation.

@@
